Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-06-06 manuscript/main.tex
Clarify bootstrap p value results
Set the y-axis range of the bootstrap distribution figures to the same values
for both validation and test data to more clearly represent the higher variance
of the test data points for natural populations. Also update the methods text
for bootstrap tests to explicitly state the meaning of the p value.

We compared the performance of different pairs of models using bootstrap tests.
For each timepoint, we calculated the difference between one model's earth mover's distance to the future and the other model's distance.
The resulting empirical distribution values less than zero when the first model outperformed the second model.
To determine whether the first model generally outperformed the second model, we bootstrapped the empirical difference distributions for n=10,000 samples and calculated the mean difference of each bootstrap sample.
We calculated an empirical p value for the first model as the proportion of bootstrap samples with mean values greater than or equal to zero.
We performed pairwise model comparisons for all biologically-informed models against the naive model (Supplemental Figs.~\ref{sup_fig:bootstrap_distributions_for_simulated_sample_3} and \ref{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}).
We also compared a subset of composite models to their respective individual models (Supplemental Table~\ref{sup_table:composite_vs_individual_model_comparison}).

>>>>

We compared the performance of different pairs of models using bootstrap tests.
For each timepoint, we calculated the difference between one model's earth mover's distance to the future and the other model's distance.
Values less than zero in the resulting empirical distribution represent when the first model outperformed the second model.
To determine whether the first model generally outperformed the second model, we bootstrapped the empirical difference distributions for n=10,000 samples and calculated the mean difference of each bootstrap sample.
We calculated an empirical p value for the first model as the proportion of bootstrap samples with mean values greater than or equal to zero.
This p value represents how likely the mean difference between the models' distances to the future is to be zero or greater.
We performed pairwise model comparisons for all biologically-informed models against the naive model (Supplemental Figs.~\ref{sup_fig:bootstrap_distributions_for_simulated_sample_3} and \ref{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}).
We also compared a subset of composite models to their respective individual models (Supplemental Table~\ref{sup_table:composite_vs_individual_model_comparison}).

### 2020-06-06 manuscript/tables/composite_vs_individual_model_comparison.tex
Clarify bootstrap p value results
Set the y-axis range of the bootstrap distribution figures to the same values
for both validation and test data to more clearly represent the higher variance
of the test data points for natural populations. Also update the methods text
for bootstrap tests to explicitly state the meaning of the p value.

\begin{tabular}{llllrr}
\toprule
    sample &  error\_type &      individual\_model &                         composite\_model &  empirical\_difference &  p\_value \\
\midrule
 simulated &  validation &          true fitness &                  mutational load +  LBI &                  0.42 &   0.9678 \\
 simulated &  validation &       mutational load &                  mutational load +  LBI &                 -1.03 &   0.0000 \\
 simulated &  validation &                   LBI &                  mutational load +  LBI &                 -0.33 &   0.0096 \\
 simulated &        test &          true fitness &                  mutational load +  LBI &                 -0.28 &   0.1421 \\
 simulated &        test &       mutational load &                  mutational load +  LBI &                 -1.11 &   0.0000 \\
 simulated &        test &                   LBI &                  mutational load +  LBI &                 -0.41 &   0.0002 \\
   natural &  validation &       mutational load &                  mutational load +  LBI &                 -0.69 &   0.0046 \\
   natural &  validation &                   LBI &                  mutational load +  LBI &                 -0.23 &   0.0027 \\
   natural &  validation &       mutational load &  mutational load + HI antigenic novelty &                 -0.31 &   0.0410 \\
   natural &  validation &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.18 &   0.0559 \\
   natural &        test &       mutational load &                  mutational load +  LBI &                  1.17 &   0.9400 \\
   natural &        test &                   LBI &                  mutational load +  LBI &                 -0.70 &   0.0000 \\
   natural &        test &       mutational load &  mutational load + HI antigenic novelty &                 -0.56 &   0.0135 \\
   natural &        test &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.24 &   0.0948 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llllrr}
\toprule
    sample &  error\_type &      individual\_model &                         composite\_model &  empirical\_difference &  p\_value \\
\midrule
 simulated &  validation &          true fitness &                  mutational load +  LBI &                  0.42 &   0.9672 \\
 simulated &  validation &       mutational load &                  mutational load +  LBI &                 -1.03 &   0.0000 \\
 simulated &  validation &                   LBI &                  mutational load +  LBI &                 -0.33 &   0.0097 \\
 simulated &        test &          true fitness &                  mutational load +  LBI &                 -0.28 &   0.1395 \\
 simulated &        test &       mutational load &                  mutational load +  LBI &                 -1.11 &   0.0000 \\
 simulated &        test &                   LBI &                  mutational load +  LBI &                 -0.41 &   0.0001 \\
   natural &  validation &       mutational load &                  mutational load +  LBI &                 -0.69 &   0.0034 \\
   natural &  validation &                   LBI &                  mutational load +  LBI &                 -0.23 &   0.0026 \\
   natural &  validation &       mutational load &  mutational load + HI antigenic novelty &                 -0.31 &   0.0420 \\
   natural &  validation &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.18 &   0.0560 \\
   natural &        test &       mutational load &                  mutational load +  LBI &                  1.17 &   0.9379 \\
   natural &        test &                   LBI &                  mutational load +  LBI &                 -0.70 &   0.0000 \\
   natural &        test &       mutational load &  mutational load + HI antigenic novelty &                 -0.56 &   0.0113 \\
   natural &        test &  HI antigenic novelty &  mutational load + HI antigenic novelty &                 -0.24 &   0.0962 \\
\bottomrule
\end{tabular}
